---
title: "Markdown Document"
author: "Kuntal Ganguly"
date: "August 15, 2017"
output:
  html_document:
    theme: cosmo
    toc: yes
  word_document: default
  pdf_document:
    toc: yes
---
* * *
# Introduction
This is an *R Markdown document*. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. 

# HTML Content
<p> This is a new paragraph written with the HTML tag 
<table border=1> 
<th> Pros </th>

<th> Cons </td>
<tr>
<td>Easy to use</td>
<td>Need to Plan ahead </td>
<tr> 
</table>
<hr/>

# Embed Code
## Set Directory
You can embed any R code chunk within 3 ticks. If you add echo=FALSE the code chunk is not displayed in the document. We can set knitr options either globally or within a code segment. The options set globally are used throughout the document. 

We set the root.dir before loading any files. By enabling cache=TRUE, a code chunk is executed only when there is a change from the prior execution. This enhances knitr performance.

```{r setup, echo=FALSE, message=FALSE, warning=FALSE} 
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_knit$set(root.dir = "/Users/kuntalg/projects/RCookbook/chapter8/") 
```

## Load data

```{r loadData, echo=FALSE}
auto <- read.csv("auto-mpg.csv")
```

<test_link>

### Plot Data
```{r plotData }
plot(auto$mpg~auto$weight)
```

### Plot with format options
```{r plotFormatData, echo=FALSE, fig.height=4, fig.width=8}
plot(auto$mpg~auto$weight)
str(auto)
```
There are `r nrow(auto)` cars in the auto data set. 